О множествах точек на плоскости с целочисленными расстояниями

### 2018-09-23 vmmsh-2018/blg.tex
[vmmsh] Bibiliography- WIP

\emph{Erdös} \emph{P.} Integral distances // Bulletin of the

@@

\emph{Anning} \emph{N. H.}, \emph{Erdös} \emph{P.}

@@

\emph{Solymosi} \emph{J.} Note on integral distances //

@@

\emph{Anning} \emph{N.} Discussions: Relating to a Geometric

@@

\emph{Harborth} \emph{H.},
\emph{Möller} \emph{M.} An

@@

\emph{Kemnitz} \emph{A.},

@@

\emph{Piepmeyer} \emph{L.} The maximum number of odd

@@

\emph{Kurz} \emph{S.}, \emph{Laue} \emph{R.} Bounds for

@@

\emph{Авдеев} \emph{Н. Н.} Некоторые примеры систем

@@

\emph{Locatelli} \emph{M.}, \emph{Raber} \emph{U.} Packing

@@

\emph{Costa} \emph{A.} Valid constraints for the point packing

@@

\emph{Markót} \emph{M. C.}, \emph{Csendes} \emph{T.} A

@@

\emph{DeGroot} \emph{C.}, \emph{Peikert} \emph{R.},
\emph{Würtz} \emph{D.} The optimal packing of ten equal

@@

\emph{Kemnitz} \emph{A.} Punktmengen mit ganzzahligen

@@

\emph{Бухштаб} \emph{А.} Теория чисел. — 1966. — С. 384.

@@

\emph{Авдеев} \emph{Н. Н.} Об отыскании множеств точек на

@@

\emph{Авдеев} \emph{Н. Н.} О множествах точек на

@@

\emph{Вавилов} \emph{В.}, \emph{Устинов}

@@

\emph{А.}

@@

\emph{Kohnert} \emph{A.}, \emph{Kurz} \emph{S.} Integral

@@

\emph{Kurz} \emph{S.} On the characteristic of integral point

@@

\emph{Harborth} \emph{H.}, \emph{Kemnitz} \emph{A.}

@@

\emph{Kanold}
\emph{H.-J.}

@@

\emph{Nozaki} \emph{H.} Lower bounds for the minimum

@@

\emph{Piepmeyer}
\emph{L.}

@@

\emph{Harborth} \emph{H.}, \emph{Piepmeyer} \emph{L.}

@@

\emph{Harborth} \emph{H.} Integral distances in point sets //

@@

\emph{Kurz} \emph{S.} Konstruktion und Eigenschaften

@@

\emph{Kurz} \emph{S.}, \emph{Wassermann} \emph{A.} On

@@

\emph{Авдеев} \emph{Н. Н.}, \emph{Семёнов} \emph{Е. М.}

@@

\emph{Kreisel} \emph{T.}, \emph{Kurz} \emph{S.} There are

@@

\emph{Brass} \emph{P.}, \emph{Moser} \emph{W. O.},
\emph{Pach} \emph{J.} Research problems in discrete

@@

\emph{Guy} \emph{R.} Unsolved problems in number theory. Т.

@@

\emph{Noll} \emph{L. C.}, \emph{Bell} \emph{D. I.} n-clusters

@@

\emph{Graham} \emph{R.}, \emph{Rothschild} \emph{B.},
\emph{Straus} \emph{E.} Are there $n + 2$ points in $E^n$ with odd

@@

\emph{Ulam} \emph{S. M.} A collection of mathematical

@@

\emph{Garibaldi} \emph{J.}, \emph{Iosevich} \emph{A.} The

@@

\emph{Garibaldi} \emph{J.}, \emph{Iosevich} \emph{A.},
\emph{Senger} \emph{S.} The Erdös Distance Problem. Т. 56. —

@@

\emph{Erdös} \emph{P.} On sets of distances of n points //

@@

\emph{Guth} \emph{L.}, \emph{Katz} \emph{N. H.} On the

>>>>

\textsl{Erdös} \textsl{P.} Integral distances // Bulletin of the

@@

\textsl{Anning} \textsl{N. H.}, \textsl{Erdös} \textsl{P.}

@@

\textsl{Solymosi} \textsl{J.} Note on integral distances //

@@

\textsl{Anning} \textsl{N.} Discussions: Relating to a Geometric

@@

\textsl{Harborth} \textsl{H.},
\textsl{Möller} \textsl{M.} An

@@

\textsl{Kemnitz} \textsl{A.},

@@

\textsl{Piepmeyer} \textsl{L.} The maximum number of odd

@@

\textsl{Kurz} \textsl{S.}, \textsl{Laue} \textsl{R.} Bounds for

@@

\textsl{Авдеев} \textsl{Н. Н.} Некоторые примеры систем

@@

\textsl{Locatelli} \textsl{M.}, \textsl{Raber} \textsl{U.} Packing

@@

\textsl{Costa} \textsl{A.} Valid constraints for the point packing

@@

\textsl{Markót} \textsl{M. C.}, \textsl{Csendes} \textsl{T.} A

@@

\textsl{DeGroot} \textsl{C.}, \textsl{Peikert} \textsl{R.},
\textsl{Würtz} \textsl{D.} The optimal packing of ten equal

@@

\textsl{Kemnitz} \textsl{A.} Punktmengen mit ganzzahligen

@@

\textsl{Бухштаб} \textsl{А.} Теория чисел. — 1966. — С. 384.

@@

\textsl{Авдеев} \textsl{Н. Н.} Об отыскании множеств точек на

@@

\textsl{Авдеев} \textsl{Н. Н.} О множествах точек на

@@

\textsl{Вавилов} \textsl{В.}, \textsl{Устинов}

@@

\textsl{А.}

@@

\textsl{Kohnert} \textsl{A.}, \textsl{Kurz} \textsl{S.} Integral

@@

\textsl{Kurz} \textsl{S.} On the characteristic of integral point

@@

\textsl{Harborth} \textsl{H.}, \textsl{Kemnitz} \textsl{A.}

@@

\textsl{Kanold}
\textsl{H.-J.}

@@

\textsl{Nozaki} \textsl{H.} Lower bounds for the minimum

@@

\textsl{Piepmeyer}
\textsl{L.}

@@

\textsl{Harborth} \textsl{H.}, \textsl{Piepmeyer} \textsl{L.}

@@

\textsl{Harborth} \textsl{H.} Integral distances in point sets //

@@

\textsl{Kurz} \textsl{S.} Konstruktion und Eigenschaften

@@

\textsl{Kurz} \textsl{S.}, \textsl{Wassermann} \textsl{A.} On

@@

\textsl{Авдеев} \textsl{Н. Н.}, \textsl{Семёнов} \textsl{Е. М.}

@@

\textsl{Kreisel} \textsl{T.}, \textsl{Kurz} \textsl{S.} There are

@@

\textsl{Brass} \textsl{P.}, \textsl{Moser} \textsl{W. O.},
\textsl{Pach} \textsl{J.} Research problems in discrete

@@

\textsl{Guy} \textsl{R.} Unsolved problems in number theory. Т.

@@

\textsl{Noll} \textsl{L. C.}, \textsl{Bell} \textsl{D. I.} n-clusters

@@

\textsl{Graham} \textsl{R.}, \textsl{Rothschild} \textsl{B.},
\textsl{Straus} \textsl{E.} Are there $n + 2$ points in $E^n$ with odd

@@

\textsl{Ulam} \textsl{S. M.} A collection of mathematical

@@

\textsl{Garibaldi} \textsl{J.}, \textsl{Iosevich} \textsl{A.} The

@@

\textsl{Garibaldi} \textsl{J.}, \textsl{Iosevich} \textsl{A.},
\textsl{Senger} \textsl{S.} The Erdös Distance Problem. Т. 56. —

@@

\textsl{Erdös} \textsl{P.} On sets of distances of n points //

@@

\textsl{Guth} \textsl{L.}, \textsl{Katz} \textsl{N. H.} On the
